Classless Java

### 2015-09-27 paper/sections/Formalization.tex
Shadow and the reviewd rule are ready to discuss together

\[ \inferrule[(ReviewedRule)]{
  IT(C_0) = \text{\emph{ann} interface } C_0 \text{ extends } \overline{C} \{
  \methods \} \\
  \methods(\m)=\method
%\\
%\Aux{tops}(\overline{C})=\C_1\ldots\C_n  
  }
{ \mBody(\m,\C_0) = \textsf{replace}(\method, %\shadow(\mBody(\m,C_1)\ldots\mBody(\m,C_n))
\shadow(m,\Aux{tops}(\Cs)) 
} \]
\subsubsection{Auxiliary function: $\tops(\Cs), \shadow(\m,\Cs),\override(\method,\method')$}

@@

The \textsf{shadow} function takes two same methods (with the same name and types of arguments), and return the method which shadows the other during inheritance.
%exmples to motivate our design
%interface A{static String m(){return "A";}}
%interface C extends A{
%	default String dm(){
%		  this.m();//wrong in java
%		  A.m();
%		  C.m();//wrong in java
%		}
%}
%
%
%(1) Static methods are not inherited. Also, if one of $\{body_1,body_2\}$ is null, \textsf{shadow} simply returns the other one. Hence

@@

\shadow()=\none\\
\shadow(\methods)=\method &\mif\ \method \in \methods, \forall \method' \in \methods\setminus\method :  \method' \subtype  \method,\\
\mbox{ otherwise}\\
\shadow(\methods)=\conflicted\mh&\mif\ \shadow(\Aux{removeBody}(\methods))=\mh\\
\Aux{removeBody}(\QM{default}\ \mh\mbox{\Q@\{return \_;\}@})
=\mh\QM;\\
\Aux{removeBody}(\mh\QM)
=\mh\QM;
\\
%\mh\mbox{\Q@\{return \_;\}@}\shadow \mh & \mif\ \mh\shadow\mh'\\
\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}\subtype \mh & \mif\ \mh\subtype\mh'\\

\T\ \m\oR\T_1\x_1\ldots \T_n\x_n\cR \subtype \T' \m\oR\T_1\x_1'\ldots\T_n\x_n'\cR & \mif\ \T\subtype \T'\\
\override(\method,\none)=
\override(\none,\method)=\method\\
\override(\method,\method')
=
\override(\method,\mh\QM;) & \method'=\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}\\
\\
\override(\method,\mh')
=\method &\mif\ \method\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@} \}\\
& \mh\subtype\mh'\\
%\textsf{shadow}(body_1, body_2)=\emptyset & \textsf{if }body_1.\textsf{modifier}=body_2.\textsf{modifier}=\textbf{static}\\
%\textsf{shadow}(body_1, body_2)=body_1 & \textsf{if }body_2=\emptyset\textsf{ or }body_2.\textsf{modifier}=\textbf{static}\\
%\textsf{shadow}(body_1, body_2)=body_2 \hspace{.1in}  & \textsf{if }body_1=\emptyset\textsf{ or }body_1.\textsf{modifier}=\textbf{static}
\end{array}
\end{equation*}

@@

\subsubsection{Auxiliary function: \textsf{replace}}

The \textsf{replace} function takes two same methods (with the same name and types of arguments), and gives the result of the first method overriding the second one.

\begin{equation*}
\begin{array}{ll}
\textsf{replace}(body_1, body_2)=body_1 & \textsf{if }body_2=\emptyset\\
\textsf{replace}(body_1, body_2)=body_2 & \textsf{if }body_1=\emptyset\\
\textsf{replace}(body_1, body_2)=body_1 & \textsf{if }body_1.\textsf{returnType}<:body_2.\textsf{returnType}\\
\textsf{replace}(body_1, body_2)=\textsf{ERROR} \hspace{.1in} & \textsf{otherwise}
\end{array}
\end{equation*}

>>>>

\[ \inferrule[(ReviewedRule)]{
  IT(C_0) = \text{\emph{ann} interface } C_0 \text{ extends } \overline{C} \{
  \methods \} 
%\\
 % \methods(\m)=\method
%\\
%\Aux{tops}(\overline{C})=\C_1\ldots\C_n  
  }
{ \mBody(\m,\C_0) = \override(\methods(\m), %\shadow(\mBody(\m,C_1)\ldots\mBody(\m,C_n))
\shadow(\m,\Aux{tops}(\Cs)))
} \]
\subsubsection{Auxiliary function: $\tops(\Cs), \shadow(\m,\Cs),\override(\method,\method')$}

@@

\shadow{} choose the most specific version of a method, that is the unique version available, or a conflicted version from a set of possibilities.
We do not model overloading, so it is an error if multiple versions are available with different parameter types.

%The \textsf{shadow} function takes two same methods (with the same name and types of arguments), and return the method which shadows the other during inheritance.
%exmples to motivate our design
%interface A{static String m(){return "A";}}
%interface C extends A{
%	default String dm(){
%		  this.m();//wrong in java
%		  A.m();
%		  C.m();//wrong in java
%		}
%}
%
%
%(1) Static methods are not inherited. Also, if one of $\{body_1,body_2\}$ is null, \textsf{shadow} simply returns the other one. Hence

@@

\shadow()=\none\\
\shadow(\method)=\method\\
\shadow(\methods)=\conflicted\mh\QM;&\mif\ \Aux{mostSpecific}(\methods))\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}\}\\
\Aux{mostSpecific}(\methods)=\method &
\mif\ \method \in \methods, \forall \method' \in \methods :  \method' \subtype  \method,\\
\T\ \m\oR\T_1\x_1\ldots \T_n\x_n\cR \subtype \T' \m\oR\T_1\x_1'\ldots\T_n\x_n'\cR & \mif\ \T\subtype \T'\\

\method \subtype
\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}=
\method\subtype\mh\QM;
\\
\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}\subtype\method=
\mh\QM;\subtype\method
\\
\override(\none,\none)=\none\\
\override(\method,\none)=\method\\

\override(\none,\method)=\method &\mif\ \method\neq \conflicted\ \mh\QM;\\
\override(\method,\method')
=
\override(\method,\mh\QM;) & \method'\in\{\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}, \conflicted\ \mh\QM; \}\\
\override(\method,\mh')
=\method &\mif\ \method\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@} \}\\
& \mh\subtype\mh'\\
%\textsf{shadow}(body_1, body_2)=\emptyset & \textsf{if }body_1.\textsf{modifier}=body_2.\textsf{modifier}=\textbf{static}\\
%\textsf{shadow}(body_1, body_2)=body_1 & \textsf{if }body_2=\emptyset\textsf{ or }body_2.\textsf{modifier}=\textbf{static}\\
%\textsf{shadow}(body_1, body_2)=body_2 \hspace{.1in}  & \textsf{if }body_1=\emptyset\textsf{ or }body_1.\textsf{modifier}=\textbf{static}
\end{array}
\end{equation*}

@@

%\subsubsection{Auxiliary function: \textsf{replace}}
%
%The \textsf{replace} function takes two same methods (with the same name and types of arguments), and gives the result of the first method overriding the second one.
%
%\begin{equation*}
%\begin{array}{ll}
%\textsf{replace}(body_1, body_2)=body_1 & \textsf{if }body_2=\emptyset\\
%\textsf{replace}(body_1, body_2)=body_2 & \textsf{if }body_1=\emptyset\\
%\textsf{replace}(body_1, body_2)=body_1 & \textsf{if }body_1.\textsf{returnType}<:body_2.\textsf{returnType}\\
%\textsf{replace}(body_1, body_2)=\textsf{ERROR} \hspace{.1in} & \textsf{otherwise}
%\end{array}
%\end{equation*}
